Age, Education, Income, and the Canadian Vote. Understanding the 2021 election.

### 2024-03-12 paper/paper.qmd
Updated cross-references and citations

The subsequent sections follow a structured format. The Data section outlines the source and variables central to our analysis. The Model section details the construction and methodology of the statistical models used. The Results section presents the key findings of our analysis, while the Discussion section critically reviews the content, addresses the implications of the results, acknowledges model limitations, and suggests potential future research directions.

@@

The data used in this paper was gathered from the 2021 Canadian Election Study (CES) hosted on the Harvard Dataverse (@citeCES) and analyzed using R (@citeR) with help from `tidyverse` (@citeTidyverse), `haven` (@citeHaven), `arrow` (@citeArrow), `rstanarm` (@citeRstanarm), `modelsummary` (@citeModelsummary), `testthat` (@citeTestthat), `here` (@citeHere), `knitr` (@citeKnitr), and `kableExtra` (@citeKableExtra).

@@

# Model

@@

\begin{align*}
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\ 
\text{logit}(\pi_i) &= \beta_0 + \beta_1 \times \text{age}_i + \beta_2 \times \text{education}_i + \beta_3 \times \text{income}_i \\ 
\beta_0 &\sim \text{Normal}(0, 2.5) \\ 
\beta_1 &\sim \text{Normal}(0, 2.5) \\ 
\beta_2 &\sim \text{Normal}(0, 2.5) \\ 
\beta_3 &\sim \text{Normal}(0, 2.5) \\ 
\end{align*}

We assume Normal priors.

# Results

@@

# Discussion

@@

The paper omits a model based on topic variables due to compute feasibility. Due how the data was stored, each variable is a number that was converted to a factor using `as_factor` from `haven` (@citeHaven). These variables would often have 3 to 5 levels for each factor or more. This lead to large models for the topic model and even the personal model. This was simply not feasible, however the data processing prior to the decision to omit the topic model and simplify the personal model was kept in the paper.

>>>>

The subsequent sections follow a structured format. @sec-data outlines the source and variables central to our analysis. @sec-model details the construction and methodology of the statistical models used. @sec-results presents the key findings of our analysis, while @sec-discussion critically reviews the content, addresses the implications of the results, acknowledges model limitations, and suggests potential research directions.

@@

The data used in this paper was gathered from the 2021 Canadian Election Study (CES) hosted on the Harvard Dataverse [@citeCES] and analyzed using R [@citeR] with help from `tidyverse` [@citeTidyverse], `haven` [@citeHaven], `arrow` [@citeArrow], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `testthat` [@citeTestthat], `here` [@citeHere], `knitr` [@citeKnitr], and `kableExtra` [@citeKableExtra].

@@

# Model {#sec-model}

@@

```{=tex}
\begin{align*}
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\ 
\text{logit}(\pi_i) &= \beta_0 + \beta_1 \times \text{age}_i + \beta_2 \times \text{education}_i + \beta_3 \times \text{income}_i \\ 
\beta_0 &\sim \text{Normal}(0, 2.5) \\ 
\beta_1 &\sim \text{Normal}(0, 2.5) \\ 
\beta_2 &\sim \text{Normal}(0, 2.5) \\ 
\beta_3 &\sim \text{Normal}(0, 2.5) \\ 
\end{align*}
```
We assume Normal priors.

# Results {#sec-results}

@@

# Discussion {#sec-discussion}

@@

The paper omits a model based on topic variables due to compute feasibility. Due how the data was stored, each variable is a number that was converted to a factor using `as_factor` from `haven` [@citeHaven]. These variables would often have 3 to 5 levels for each factor or more. This lead to large models for the topic model and even the personal model. This was simply not feasible, however the data processing prior to the decision to omit the topic model and simplify the personal model was kept in the paper.
